Bare Demo of IEEEtran.cls\\ for IEEE Conferences

### 2016-11-30 paper.tex
Revise figure references
They are hard-wired, maybe wrong and should anyway be substituted by references.  Check it out @mariosky

\section{Experiment}
\label{sec:exp}
The aim of this research is to evaluate the use of keyboard
and mouse dynamics as an appropriate sensory input for an affective recognition
system. The context of use is a learning environment for programmers. In
particular for learning activities consisting in writing short programs
interactively. An experimental approach was adopted with this aim. Sensory and
quantitative data was collected from learners as they were enrolled in a basic
course of Python programming. This data was then pre-processed using the method
described earlier, and together with the quantitative data obtained from users,
classifiers were trained and validated. The results were then compared and came
to conclusions regarding the effectiveness of the method. The goal given to
subjects was to solve as many exercises as they could in a period of two weeks.
There was neither time limit nor a minimum amount of time required for a
participant while trying to solve the exercises or complete the tutorial. The
participants were able to stop and resume their interaction with the system at
any time.

@@

A tutorial was developed to
obtain the necessary data using Protoboard, a web-based programming learning
environment (the latest version can be found online at
http://python.protoboard.org/). Protoboard has the functionality described in
the proposed method and shown schematically in Figure 1. Users-log in to
Protoboard using their account credentials from a popular social network
(Facebook).  The web tutorial begins with three introductory videos that explain
the fundamentals of programming in Python, and how to solve the programming
exercises in the course. What follows after these videos, are 13 programming
exercises that the students need to solve in consecutively. Exercises are of
incremental difficulty. In Figures 2 and 3, the interface of this platform is
presented. For this experiment Protoboard was configured to allow unlimited
tries to solve an exercise.

>>>>

\section{Experiment}
\label{sec:exp}
The aim of this research is to evaluate the use of keyboard
and mouse dynamics as an appropriate sensory input for an affective recognition
system. The context of use is a learning environment for programmers. In
particular for learning activities consisting in writing short programs
interactively. An experimental approach was adopted with this aim: Sensory and
quantitative data was collected from learners as they were enrolled in a basic
course of Python programming. This data was then pre-processed using the method
described earlier in Section \ref{sec:method}, and together with the quantitative data obtained from users,
classifiers were trained and validated. The results were then compared
and we arrived to some conclusions regarding the effectiveness of the method. The goal given to
subjects was to solve as many exercises as they could in a period of two weeks.
There was neither time limit nor a minimum amount of time required for a
participant while trying to solve the exercises or complete the tutorial. The
participants were able to stop and resume their interaction with the system at
any time.

@@

A tutorial was developed to
obtain the necessary data using Protoboard, a web-based environment,
whose latest version can be found online at
http://python.protoboard.org/, used for learning to
program. Protoboard has the functionality described in Section
\ref{sec:method} and shown schematically in Figure 1. % This should be
                                % a reference and I'm not sure which
                                % one, if it's now Fig 1 or 2. - JJ
Users log in to 
Protoboard using their account credentials from a popular social network
(Facebook).  The web tutorial begins with three introductory videos that explain
the fundamentals of programming in Python, and how to solve the programming
exercises in the course. What follows after these videos, are 13 programming
exercises that the students need to solve in consecutively. Exercises are of
incremental difficulty. In Figures 2 and 3, % 3 is keystroke
                                % dynamics. Please revise all these
                                % Figure thing. 
 the interface of this platform is
presented. For this experiment Protoboard was configured to allow unlimited
tries to solve an exercise.
